%% 
%% Copyright 2007, 2008, 2009 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%% 

%% Template article for Elsevier's document class `elsarticle'
%% with numbered style bibliographic references
%% SP 2008/03/01

\documentclass[preprint,12pt, a4paper]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{hyperref}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
%\usepackage{lineno}

\journal{Software Impacts}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

\title{MinViME/Minium Viable Model Estimator}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \address[label1]{}
%% \address[label2]{}

\author{John Hawkins}

\address{}

\begin{abstract}
%% Text of abstract 
MinViME is a python package and web application that allows developers
to estimate the performance characteristics of a Minimum Viable Machine Learning Model for a specific
problem. It has been used to evaluate the feasibility of machine learning projects
, prioriotize among projects, and run simulations to explore the
structure of the difficulty landscape across multiple dimensions
of business problems.

\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
data science \sep machine learning \sep project management \sep estimation

%% PACS codes here, in the form: \PACS code \sep code

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

\end{keyword}

\end{frontmatter}

%\linenumbers

\noindent

\section{Introduction}

Machine learning projects are undertaken with an expectation
that they will add some value to the process in which they will be used.
The value relies on both the performance characteristics of the model
and the characteristics of the business application. In spite of the
feasibility being heavily dependant on the business characteristics of
the problem there has not been a consistent effort to provide tools and
techniques to estimate it.

The machine learning literature includes implementation considerations
for improving model performance. For example, through development of domain 
specific methods such as designing loss functions for specific applications 
(See \cite{Johnson19}, \cite{Hennig2007}). Historically, the field of  
cost sensitive learning \cite{Domingos1999,Margineantu2000,Elkan2001,Tian+Zhang2019}
developed general techniques to learn a solution that is tuned to the
specifics of business problem (for example \cite{Fatlawi2017}). 
In general, you can achieve the same outcome by learning a well calibrated 
probability estimator and adjusting the decision threshold
on the basis of the cost matrix \cite{Nikolaou2016}.
The cost matrix approach to analysing a binary classifier can be also be used to estimate its expected ROI \cite{Ylijoki2018}.

These approaches allow you to improve and customise a model for a given application, 
but they do not help you decide if the project is economically viable in the first place. 
There have been extensive efforts to characterise project
complexity in terms of data set requirements for given performance 
criteria \cite{Raudys1991}, however the task of determining these criteria 
from business requirements has not, to our knowledge, been addressed.
Fortunately, some of the machinery for the cost matrix
analysis can be used in reverse to estimate the baseline performance 
a model would require to reach minimal ROI expectations.

We use the framework of a cost matrix to develop a method for estimating 
the minimum viable binary classification
model that satisifies a quantitative definition of the business requirements. 
We demonstrate that a lower bound
on \textit{precision} can be calculated \textit{a priori}, 
but that most other metrics require knowledge of either the expected number
of false positives or false negatives. We devise an additional 
\textit{simplicity} metric which allows for direct
comparison between machine learning projects purely on the basis of the business criteria. Finally, we demonstrate
that lower bounds on the AUC and other metrics can be estimated through numerical simulation of the ROC plot.

We use the minvime ROC simulator to conduct a range of experiments to explore the manner in which the minimum viable
model changes with the dimensions of the problem landscape.
The results of these simulations are presented in a manner to help develop
intuitions about the feasibility of machine learning projects.




\textbf{Main text}\\
Maximum 3 pages (excluding metadata, tables, figures, references)\\

\noindent
The description of your software  shall include:
\begin{itemize}
\item A short description of the high-level functionality and purpose of the software for a diverse, non-specialist audience
\item An Impact overview that illustrates the purpose of the software and its achieved results:
\begin{itemize}
\item[-] Indicate in what way, and to what extent, the pursuit of existing research questions is improved. 
\item[-] Indicate in what way new research questions can be pursued because of the software.
\item[-] Indicate in what way the software has changed the daily practice of its users.
\item[-] Indicate how widespread the use of the software is within and outside the intended user group.
\item[-] Indicate in what way the software is used in commercial settings and/or how it led to the creation of spin-off companies (if so).
\end{itemize}
\item Mentions (if applicable) of any ongoing research projects using the software. 
\item A list of all scholarly publications enabled by the software.
\end{itemize}


\section*{Acknowledgements}
\label{}

Thanks to the Translational Artifical Intelligence Group.

\section*{References}

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

%% \section{}
%% \label{}

%% References:
%% If you have bibdatabase file and want bibtex to generate the
%% bibitems, please use
%%
%%  \bibliographystyle{elsarticle-num} 
%%  \bibliography{<your bibdatabase>}

\bibliographystyle{elsarticle-num}

\bibliography{refs}

%% else use the following coding to input the bibitems directly in the
%% TeX file.


\section*{Illustrative Examples}

Optional : you may include one explanatory  video that will appear next to your article, in the right hand side panel. (Please upload any video as a single supplementary file with your article. Only one MP4 formatted, with 50MB maximum size, video is possible per article. Recommended video dimensions are 640 x 480 at a maximum of 30 frames / second. Prior to submission please test and validate your .mp4 file at  \url{http://elsevier-apps.sciverse.com/GadgetVideoPodcastPlayerWeb/verification} . This tool will display your video exactly in the same way as it will appear on ScienceDirect. )


\section*{Required Metadata}
\label{}

\section*{Current code version}
\label{}

\begin{table}[!h]
\begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
\hline
\textbf{Nr.} & \textbf{Code metadata description} & \textbf{} \\
\hline
C1 & Current code version & V1.0.0 \\
\hline
C2 & Permanent link to code/repository & https://github.com/john-hawkins/minvime \\
\hline
C3  & Permanent link to Reproducible Capsule & https://pypi.org/project/minvime/ \\
\hline
C4 & Legal Code License   & MIT \\
\hline
C5 & Code versioning system used & git \\
\hline
C6 & Software code languages, tools, and services & Python3\\
\hline
C7 & Compilation requirements, operating environments \& dependencies & Python3, Flask, numpy, pandas, matplotlib\\
\\
\hline
C8 & If available Link to developer documentation/manual & \\
\hline
C9 & Support email for questions & \\
\hline
\end{tabular}
\caption{Code metadata (mandatory)}
\label{} 
\end{table}

\end{document}
\endinput
%%
%% End of file `SoftwareX_article_template.tex'.
